Characteristic polynomials of p-adic matrices

### 2017-04-16 charpoly/charpoly.tex
Adding some responses to the reviewer notes

      \xavier{I think that the cost is $O(n^2)$ because it corresponds to an elementary operation of rows/columns. Is that correct?}

@@

      \xavier{I do not really understand this remark. I mean: once we have the Frobenius invariants, the characteristic polynomial is just the product of them, isn't it?}

@@

      \xavier{FWIW, I wrote a proof in my lecture at JNCF. Maybe we can just cite it.}

@@

      \xavier{Ok but it is not important (since we are just interested in the result). Should we really say more about that? (In practice, I think that we used the \texttt{adjoint} method of \textsc{sage}.)}

@@

\item \tdo{Make the relationship between $P$, $Q$ and $R$ in Theorem 4.1 explicit.}\\
      \xavier{\done{Done.} I've rewritten everything in terms of $P$ and $Q$ only.}

@@

      \xavier{Maybe we should instead remove any mention to the tangent space: it's not really necessary.}

>>>>

      \xavier{I think that the cost is $O(n^2)$ because it corresponds to an elementary operation of rows/columns. Is that correct?} \\
      \david{I agree.  I think we just need to explain that the matrix products are just notational, not actually computed.}

@@

      \xavier{I do not really understand this remark. I mean: once we have the Frobenius invariants, the characteristic polynomial is just the product of them, isn't it?}\\
      \david{Agreed.  I think I can clarify the language somewhat, but there's no real work to be done.}

@@

      \xavier{FWIW, I wrote a proof in my lecture at JNCF. Maybe we can just cite it.}\\
      \david{Citing it seems reasonable.}

@@

      \xavier{Ok but it is not important (since we are just interested in the result). Should we really say more about that? (In practice, I think that we used the \texttt{adjoint} method of \textsc{sage}.)}\\
      \david{I had the same reaction when I first saw the results.  I think we can say something to make clearer that it doesn't matter how it is computed.}

@@

@@

      \xavier{Maybe we should instead remove any mention to the tangent space: it's not really necessary.}\\
      \david{That's probably a good idea.  We'll have to make a remark about ignoring the leading monic term.}
